\documentclass[12pt]{article}

\usepackage{url}
\usepackage{amsmath}
\usepackage{bbm}

% take more advantage of the size of paper
\addtolength{\topmargin}{-2cm}
\addtolength{\textheight}{4cm}
\addtolength{\evensidemargin}{-2cm}
\addtolength{\oddsidemargin}{-2cm}
\addtolength{\textwidth}{4cm}

% some standard packages
\usepackage{times}
\usepackage{graphicx}

% convenient abbreviations
\newcommand{\EQ}{\begin{equation}}
\newcommand{\EN}{\end{equation}}
\newcommand{\HDD}{\mbox{\it HDD}}


\pagestyle{empty}	%get rid of page numbers

\begin{document}

\title{Personal Statement for Student Travel Grant}
%\author{Yi Qian}{}{}
\date{}
\maketitle
%\thispagestyle{empty}

%\section{Abstract}
%\label{Abstract}

%\large
%{\LARGE \emph{Abstract}}
%large
%\bigskip

I am writing to apply for the ACM CCS student travel grant to attend the Cloud Computing Security Workshop (CCSW14). I am the first author of the accepted paper {\it Streaming Authenticated Data Structures: Abstraction and Implementation}, and will be presenting my paper at the workshop if offered the grant. This work is an extension of Professor Charalampos Papamanthou's paper (EUROCRYPT 2013) on {\it streaming authenticated data structures} (SADS). It presents an {\it abstract} SADS construction that can use any hash function satisfying properties that we formally define. This leads to a simpler exposition of the fundamental ideas of the EUROCRYPT paper, and to a practical implementation of a SADS that employs an efficient hash function.

It is my second year as a computer science PhD student at University of Maryland, College Park. Apart from the problems in cloud computing security, I also enjoy working on applied cryptology in general. I am excited about the prospect of sharing my work with the community, and exploring the various research work by other lecturers at the workshop. There is no doubt that this will be a great opportunity for me to learn the latest trends, as well as get to know many famous scholars, in this area. I believe attending CCSW14 will bring great inspiration and motivation in my future research.

I am truly looking forward to attending CCSW14 and presenting my work. Unfortunately, I would be unable to participate in the workshop without this travel grant. Thank you very much for your consideration of my application.

\bigskip
Sincerely,\\


\bigskip
Yi Qian

September 10, 2014

\end{document}



